Lens Modeling in \sw

### 2014-01-12 text/ms.tex
finished setup
plaing around with contour plots
layout of intro, changes to scirpts, made class copatible to setlength
a few words on sl, added bib entries
plot gen script working
added results for test1, inkl autogenerated tables
ideas for results section
t1
further work
moar results
minor ajustments to plots and tables
small fixes on text, tables, plots
rearranged figure placement
suppressing figures
added pdf
Commented out images
testing 2
editing sec3
editing sec3

more edits

editing sec3 - added proper def of theta_e_sim, theta_e

editing sec3

%%% PACKAGES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath}
\usepackage{xspace}   % fixes spaces after custom commands
\usepackage{float}    % exact placement of figures (using \begin{figure}[H])
%\usepackage{caption}  % better captions for floats

%%% DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\half{{\textstyle\frac12}}
\newcommand{\spl}{SpaghettiLens\xspace}
\newcommand{\sw}{SpaceWarps\xspace}

%%% DOCUMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\input{tex/abstract}
\input{tex/intro}
\input{tex/theory}
\input{tex/spaghetti}
\input{tex/results}
\input{tex/outlook}

\input{tex/appendix}

>>>>

\usepackage{amsmath}
\usepackage{xspace}   % fixes spaces after custom commands
\usepackage{float}    % exact placement of figures (using \begin{figure}[H])
\usepackage{color}  % well... color...
\usepackage{setspace}    % remove this pgk for final compile!! 
\usepackage{subfigure}

\usepackage{longtable}   % those two to generate the 2 ol table
\usepackage{multicol}

\def\half{{\textstyle\frac12}}
% makes it easier to have consistent writing, and easy change if needed
\newcommand{\spl}{SpaghettiLens\xspace}
\newcommand{\sw}{SpaceWarps\xspace}

% shortcut for einstein radius (Text Greek Full Math)
\newcommand{\ER}{Einstein radius\xspace} % text
\newcommand{\ERg}[1][]{$\Theta_{\text{E#1}}$\xspace} % er in textmode with greek
\newcommand{\ERf}[1][]{Einstein radius $\Theta_\text{E#1}$\xspace} % full output
\newcommand{\ERm}[1][]{\Theta_\text{E#1}} % mathmode with greek symbol

%shortcuts for kappa
\newcommand{\kenc}[1][r]{$\kappa_\text{encl}(#1)$\xspace}
\newcommand{\kap}[1][r]{$\kappa(#1)$\xspace}

% shorcuts for refs (use capital for beginning of sentence)
% first 3 are for the real layz people..
\newcommand{\fref}[1]{\ref{fig:#1}}
\newcommand{\sref}[1]{\ref{sec:#1}}
\newcommand{\tref}[1]{\ref{tab:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\Figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\Secref}[1]{Section~\ref{sec:#1}}
\newcommand{\Tabref}[1]{Table~\ref{tab:#1}}

% shortcut for ASW000xxxx
\newcommand{\asw}[1]{ASW000#1\xspace}

\newcommand{\model}[2][Model~]{#1#2\xspace}

%degrees
\newcommand{\dgr}{^{\circ}}

% todo annotations on side in red. easy to search for at the end
\newcommand{\todo}[2][red]{%\marginpar{\raggedright\scriptsize\sffamily\textcolor{red}{#1}}}

\textcolor{#1}{\textbullet}%
\marginpar{\colorbox{#1}{\parbox{\marginparwidth}{%
\setstretch{0.4}\sffamily\textcolor{black}{\scriptsize{#2}}}}}}

\newcommand{\needfig}[1][]{%
\colorbox{yellow}{\parbox{0.5\textwidth}{%
\vspace{0.5cm}\setstretch{0.5}\textcolor{black}{\scriptsize{fig #1}}\vspace{0.5cm}}}%
\marginpar{\colorbox{yellow}{\parbox{\marginparwidth}{%
\setstretch{0.4}\sffamily\textcolor{black}{\scriptsize{fig}}}}}}

\setlength{\marginparsep}{0mm}
\setlength{\marginparwidth}{2.2cm}

\newcommand{\needcite}[1][]{\todo[green]{cit #1}}
\newcommand{\needref}[1][]{\todo[cyan]{ref #1}}
\newcommand{\needchk}[1][]{\todo[red]{chk #1}}

\newcommand{\hr}{\vspace{5mm}\noindent\rule{0.8\textwidth}{0.4pt}\vspace{5mm}}

@@

\begin{abstract}
In Spacewarps, volunteers are invited to search CFHTLS sky survey for
lens candidates.  Here we report on a system that allows experienced
volunteers to model lens candidates.  A sample of 29 simulated lenses
were modeled, each multiple times.  The quality of the models was then
examined in different ways.  In particular: (i)~the image parities and
time arrivals were identified correctly in most cases, but not
always; (ii)~the mean convergence (equivalent to the enclosed mass)
was quite well constrained in the image region; (iii)~the performance
of experienced volunteers was comparable to professionals.
\end{abstract}

\keywords{}
\section{Introduction}

Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.

There are many manifestations of gravitational lensing in astrophysics,
but the most spectacular are multiple images.  Gravitational lensing
depends on the sky-projection mass density, and this fact has a
counter-intuitive consequence: nearby galaxies do not produce multiple
images, because their projected density is not high enough, but beyond
100~Mpc or so, most galaxies are potential lenses.  Even so, for a
potential lens to really act as a lens, a background source in the close-by
region is required.  So, in practice galaxies are very rarely observed
as lens.  The same tendency applies to clusters of galaxies, but since
clusters are bigger, they are more likely lens-like.

In lensing galaxies, the observable features usually involve a single
object multiply imaged.  It is therefore desirable to have large
numbers of lenses, and this is the strategy researchers are following.  The
largest single study so far uses 58 lenses \citep{2009ApJ...703L..51K}.
Other studies have compared lens models in more detail with stellar
mass \citep{2011ApJ...740...97L} or used time-delay information from
lensed quasars to infer the Hubble time
\citep{2008ApJ...679...17C,2010ApJ...712.1378P}.

The trend is clear: researchers want to find many more lenses and
model them in more sophisticated ways.

\begin{figure}
\centering
\includegraphics[width=.8\hsize]{fig/lenssky.png}
\caption{Sky distribution of 398 published lenses considered secure as
  of September 2013 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

A good summary of the observational situation is offered by
Figure~\ref{fig:masterlens}, which shows known secure multiply-imaging
lenses.  The non-uniformity on the sky is not intrinsic, it just
indicates the density of deep surveys up to 2013.  At HST resolution,
of order 1~square degree of sky must be searched to find a lens.
Older ground-based surveys yield a lens per roughly 10~square degree
of survey area.  By the large surveys starting now
(DES\footnote{\tt http://pan-starrs.ifa.hawaii.edu} or
PanStarrs\footnote{\tt http://www.darkenergysurvey.org}) the expected
yield is something in between.  Given their unprecedented survey area,
these are likely to yield thousands of lenses.  Over the 2020s,
LSST\footnote{\tt http://www.lsst.org/} can be expected to give us ten
thousand lenses.

The question now arises: can lenses be found and modeled
automatically in large surveys?  Work using software robots
\citep{2009ApJ...694..924M} gives some interesting and unexpected
results.  In clean lensing system in uncrowded fields with high
signal-to-noise, the robots do very well.  In most situations,
however, robots miss lenses (low completeness) or contaminate the
results with non-lenses (low purity).  Robots can be made to
prioritize completeness or purity, but they cannot deliver both.

In response to the lessons learned from automated lens searches, the
{\em Spacewarps\/} project\footnote{\tt http://www.spacewarps.org} 
(Saha is a co-investigator) has been launched.  {\em Spacewarps\/} is
part of the {\em Zooniverse\/} family of citizen-science
projects,\footnote{\tt http://www.zooniverse.org} where members of the
public are invited to analyze different kinds of scientific data which
are too difficult for robots and too large for specialists.  In {\em
 Spacewarps\/} itself, since the launch in May 2013, $\sim100$ square
degrees (or a quarter of a percent of the sky) has been examined.  The
survey is divided into patches of $440\times 440$ pixels, each of
which is seen by ten volunteers.  Simulated lenses are mixed in with
the data, both to help train volunteers on what to look for, and to
estimate completeness and purity.  A list of candidates is being
processed, but intermediate results show some very good candidates, as
well re-discoveries of a few known lenses.

These encouraging results now raise the question: could modeling of
the lenses also be done by volunteers?  Modeling is a much more
difficult task than searching for lens candidates, as it requires some
expert knowledge.  Nonetheless, a panel of the {\em Spacewarps\/}
volunteers is quite experienced from earlier projects, having spent a
thousand hours or more with data.  Some of these experienced
volunteers are very interested in more demanding projects.  This also
is a general trend \citep[cf.][]{Khatib22112011}.  The present project
then suggests itself.

The purpose of this study was to provide a means to model a large number of gravitational lenses by showing that gravitational lens modeling can be learned / done by volunteers.
We suggest, that volunteers will be as successful as professionals with modeling if provided with an easy to use tool with visual feedback (What you see is what you get, WYSIWYG) and a minimal set of instructions.
Volunteers will then crowd work (using buzz word here ;) ) / work collaborative on modeling lenses from several sources / groups at a central place.
Since this is an iterative learning process, the more involved volunteers will quickly gain knowledge that can be passed down to new volunteers.
That creates a social structure that scales well with the number of volunteers, as other projects\needcite have already shown.
Finding people working as volunteers has been shown to be successful last but not least by \sw and the whole galaxy zoo project.
To test the people's abilities, we investigated the performance of a few volunteers modeling a set of simulated lenses.
We tested the ability to correctly identify lensed images and reproduce similar mass map of the lens.

\section{A lens modeling program}

It is well known that making a scientific contribution is a central
motivation cited by citizen-science volunteers.  So for a lens
modeler in a citizen-science project, nobody wants that it should
sacrifice scientific usefulness in order to be fun to use.  That said,
being aesthetically pleasing and having a short initial learning curve
are also essential qualities.  Also desirable is that the user is
encouraged/challenged to go deeper and wider into the subject.
Yet another aspect is enabling small incremental contributions
by different people.  \spl tries to address all of these.

\subsection{Theory: Fermat's Principle} \label{sec:Fermat}

There are several ways to understand the formation of arcs and
multiple images in gravitational lensing.  We will follow some ideas
originally introduced by \cite{1986ApJ...310..568B}, based on Fermat's
principle.  The key to this approach is an abstract construct called
the {\em arrival-time surface.}  This surface cannot itself be
observed, but several observable quantities can be derived from it.

Consider a gravitational lens.  As in most astrophysical lensing, this
lens is `thin' along the line of sight, and effectively lies on a
plane.  Let $x,y$ be coordinates on this plane.  These coordinates
measure ordinary physical lengths (meters, etc) on the lens plane.
Let there be a point source of light at $x=0,y=0$ but far behind the
lens plane.  Now imagine a light ray coming from the source to the
lens plane $(x,y)$ and then changing its path to reach the observer.
The observer would see the source apparently behind $(x,y)$ the
lens.  If this happened, the light ray would have taken a longer path
than having come directly to the observer.  The geometrical path
difference would be $\propto x^2 + y^2$ for small angles.  Let us
define
\begin{equation} \label{eq:Ageom}
A_{\rm geom}(x,y) = \half(x^2 + y^2) \,.
\end{equation}
As written, this looks an area.  But we can also think of it as a
time delay introduced by the light ray bending --- with an unwritten
constant factor.  That factor is basically the lens distance divided by the
speed of light; the precise expression has to take the expansion of
the Universe into account, and is given in the Appendix.  The top part
of \figref{arriv} shows what $A_{\rm geom}$ looks like: it is
just a paraboloid.  The minimum of the surface is at the source, and
that is where, according to Fermat's principle, the image will be.
The rest of the arrival-time surface is just an imaginary surface.

\begin{figure}
\centering
\includegraphics[height=.3\vsize]{fig/arriv1.png}
\includegraphics[height=.3\vsize]{fig/arriv2.png}
\includegraphics[height=.3\vsize]{fig/arriv3.png}
\caption{Arrival-time surfaces, with contour levels of equal arrival
  time.  The upper surface is with no lens.  The middle surface is
  when a circular lensing mass (offset from the source) is added; a
  maximum, a minimum and a saddle point can be seen.  The last surface
  is the result of an elongated lensing mass; a maximum, two minima
  and two saddle points can be seen.
}
\label{fig:arriv}
\end{figure}

The geometrical time delay \eqref{eq:Ageom} is not the only one.  The
warping of space by a gravitational field introduces a further time
delay $A_{\rm grav}$.  The arrival time of the light ray, compared to
what it would have been with no lensing, is
\begin{equation} \label{eq:Aarriv}
\hbox{arrival time} = A_{\rm geom} + A_{\rm grav} \,.
\end{equation}
We can also express $A_{\rm grav}$ as an area, with the same implicit
constant factor that makes it a time.  The expression, however, is
more complicated.  We first introduce the notation $\nabla^2 f(x,y)$
to denote
\begin{equation}
 \frac{ f(x+\Delta x, y) + f(x-\Delta x, y) +
        f(x, y+\Delta y) + f(x, y-\Delta y) - 4 f(x,y) }
      {\Delta x \; \Delta y}
\end{equation}
in the limit of $\Delta x,\Delta y$ small.  Then we write the
projected mass density of the lens, which would be in $\rm
kg\,m^{-2}$, in special units (given in the Appendix) such that the
surface density becomes a dimensionless field $\kappa(x,y)$.  Then
\begin{equation} \label{eq:Poisson}
\nabla^2 A_{\rm grav}(x,y) = -2\kappa(x,y) \,.
\end{equation}
Note that $A_{\rm grav}(x,y)$ is not given explicitly in terms of
$\kappa(x,y)$, but as a differential equation that must be solved.
Equations of the type \eqref{eq:Poisson} are, however, well known (as
Poisson's equation in two dimensions), and there are techniques for
solving them.  Incidentally, $\kappa$ has a second meaning, as well as
being a dimensionless form of the projected density: it also
measures how a bundle of light rays is brought together by
gravitational lensing, and is called the {\em convergence}.

What is the effect of mass on the arrival-time surface?  If the mass
distribution $\kappa(x,y)$ is circular, $A_{\rm grav}(x,y)$ will have
a peak at the center of that circle.  But if the mass is not precisely
in front of the source, the arrival-time surface will not be circular
any more.  The result is illustrated in the middle part of
\figref{arriv}.  In addition to the maximum, there is now a
minimum and a saddle point.  According to Fermat's principle, images
appear at maximum and saddle points as well as minimum.  If the mass
distribution is non-circular, more images can appear.  The lower
example in \figref{arriv} shows the arrival-time surface due
to an elongated mass.  There is still a maximum, part of an elongated
hill, and around it there are two minima and two saddle points.

So far we have considered a single point source.  What if there is an
extended source?  To understand this, let us consider what happens if
we move the original point source slightly, or equivalently, keep the
original point source behind $x=0,y=0$ and move the lens slightly.
The contours of constant arrival time will naturally move slightly,
and so will the images.  The movement of the contours will be most
noticeable where the contours are far apart, that is where the
arrival-time surface is nearly flat.  As is evident from
\figref{arriv}, this is the region where the minimum and saddle
points lie, or near the images.  In this region, points on the source
that are close together produce images that are comparatively far
apart.  In other words, the image is highly magnified.  In summary,
lower curvature in the arrival-time surface for a point source implies
larger magnification of an extended source.  Conversely, where the
arrival-time surface is strongly curved, the image will be
demagnified.  We see from \figref{arriv} that the arrival-time
surface tends to be highly curved near the maximum.  Hence maximum tend
to be demagnified.  In practice, maxima of the arrival time are nearly
always too faint to see. The minima and saddle points dominate.

In the lensed examples in \figref{arriv}, the maximum in each
case is evident, but how can we distinguish the minima from the saddle
points?  The key is to examine the contours of equal arrival time.
Contour curves loop around a minimum or a maximum, but near a saddle
point, the contours do not loop around, instead they approach and then
pull away.  The contour curve precisely level with a saddle point
forms an X at the saddle point.  In \figref{arriv}, one such X
is evident.  In other cases the X contour passing through the saddle
point is not itself plotted, but we can tell by the other contours where
the X would be.  These self-crossing contours will play a special role
in the following.

\subsection{\spl} \label{sec:SpaghettiLens}

\spl implements the ideas of the arrival-time surface into a modeling
program.

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006941_input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007022_input.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006919_input.png}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  }
  \label{fig:input-spag}
\end{figure}

The first modeling step with \spl is for the user to call up the \sw
of interest, and make an educated guess for the topography of the
arrival-time surface --- specifically, the locations of the maxima,
minima and saddle points that correspond to images of the brightest
part of the source.  Input is given by tracing a proposal for the
saddle-point contours.  \Figref{input-spag} shows some example
inputs --- and incidentally also indicates the origin of the name
\spl.

\spl, as implemented so far, assumes that the lens is dominated by a
single galaxy, and that the center of that galaxy is the sole maximum.
Once the maximum has been identified, we wish to characterize the rest
of the arrival-time surface in relation to it.  From geometry, any
surface that has a central maximum and goes high at the edges must
have a lima\c con-like contour, meaning a two-looped curve with one
loop inside the other.  The maximum lies within the inner loop, a
minimum lies between the two loops, and a saddle point lies at the
self-intersection of the contour.  The top panel of
\figref{input-spag} shows an example: red marks a suggested
maximum, green a saddle point, and blue a minimum.  (The small pink
dots are just help sketch the proposed contour.)  The middle and lower
panels of \figref{input-spag} show a more complex situation.
The minimum has split into three images: two new minima with a saddle
point in between.  In this situation the contour through the new
saddle point forms a figure of eight, its two loops enclosing the two
new minima.  The configuration of a lima\c con, possibly with a figure
of eight inside, suffices to give a preliminary description of the
arrival-time surface for nearly all cases where the lens is dominated
by one galaxy, and the source is a single small object.

The exact placement of the pink spaghetti loops shown in
\Figref{input-spag} has no significance.  Their utility is
just to help mark up the image as maximum, minima and saddle points.
As the figure suggests, the marking up can be done very easily with a
mouse.  Human intuition is required to (a)~identify lensed images and
separate them from other background light sources, and (b)~classify
and order images according to arrival time.  But the computer helps by
allowing only valid lensing configurations to be entered, and ensuring
that the odd image theorem\needcite is taken care of.

In the second modeling step, once the user has sketched a proposed
spaghetti configuration, \spl sends the input to its server-side
modeling engine, called GLASS.  The task of GLASS is to find a mass
distribution $\kappa(x,y)$ that exactly reproduces the locations of
the maximum, minima and saddle points. Now, this criterion by itself
is extremely under-determined --- there are infinitely many mass
distributions that will reproduce a given set of maxima, minima and
saddle points, but typically they (a)~produce lots of extra images,
and (b)~look very unlike galaxies.  Additional assumptions (a prior)
are necessary.  GLASS uses a prior based on suggestions by
\cite{1997MNRAS.292..148S}.
\begin{enumerate}
\item The mass distribution is built out of non-negative tiles of
  mass.  (Sometimes these tiles are called mass pixels, but we should
  emphasize that they are unrelated to image pixels, and are much
  larger.)
\item There is a notional lens center, say $(x_0,y_0)$ which is
  identified with the maximum of the arrival time.  The source can
  have an arbitrary offset with respect to the lens center.
\item The mass distribution must be centrally concentrated, in two
  respects.  First, the circularly averaged density must fall away
  like $$ \left[(x-x_0)^2+(y-y_0)^2\right]^{-1/2}$$ or more steeply.
  Second, the direction of increasing density at any $(x,y)$ can point
  at most $45^\circ$ away from $(x_0,y_0)$.
\item The lens must be symmetrical with respect to $180^\circ$ rotations
  about $(x_0,y_0)$.  This symmetry assumption can be relaxed if the
  user wishes.
\end{enumerate}
There are still infinitely many models that satisfy both data and
prior constraints, but now they are more credible as galaxy lenses.
It is then possible to generate an ensemble of models.  The sampling
technique used by GLASS is described in \citep{Lubini2012}, and
improves upon earlier techniques \citep{2000AJ....119..439W,Saha2004}.
Typically, ensembles of 200 models are used.  That is to say, what we
call a \spl model is really the mean of an ensemble of 200 models, and
its estimated uncertainty is the range covered by the whole ensemble.

In the third modeling step, having generated a model ensemble, \spl
post-processes it to present results and diagnostics to the user for
inspection. This takes the form of three figures.
\begin{enumerate}
\item A gray scale plus contour map of the mass distribution.
\item A contour map of the arrival-time surface.
\item A synthetic image of the lensed features.
\end{enumerate}
After examining this feedback, the user can archive the results for
discussion, or modify their input and try again, or discard the
attempt altogether.

The fourth modeling step is discussion among modelers and iteration
on the model.  Any archived model can be revised by another user: they
can modify the spaghetti configuration slightly or drastically, or
change options like the size of the mass tiles.  Particularly
interesting lens candidates lead to trees of models in this way.
Forum discussion then prunes the tree, focusing attention on one or a
few models.

\section{A lens modeling challenge} \label{sec:mod_challenge}

% \subsection{\sw} \label{sec:SpaceWarps} some words about \sw

Interested volunteers from the \sw forum were initially introduced to
\spl through a video tutorial and by videocon.  After this
introductory stage, a modeling challenge was presented.  This
consisted of 29 simulated lenses (sims) covering a range of lensing
configurations.

The \sw sims were generated by AM, in consultation with PM and AV.
To estimate the performance of the volunteers and the quality of the generated models, two analysis  were done.
The first analysis tested the correct identification and ordering of lensed images.
The second one compared the mass distribution of the lens $\kappa(x, y)$ of the generated models to the mass distribution of the simulations.

\subsection{The simulated lenses} \label{sec:sims}

For the sake of blind testing, the information in this section was
revealed neither to RK, while choosing the challenge set of 29 sims,
nor to the modelers (volunteers EB, CC, CM, JO, JW and `expert
modeler' PS) until the modeling stage was done.

The sims were produced using {\tt gravlens}
\citep{2001astro.ph..2341K,2001astro.ph..2340K}. They were of three
kinds, as follows.

\begin{enumerate}
  \item Imitating lensed quasars: having a singular elliptical
    isothermal lens (SIE) plus constant external shear, and a circular
    Gaussian source.
  \item Emulating lensed galaxies: similar to the above, but with an
    elliptical de Vaucouleurs source.
  \item Resembling cluster lenses: having a source as above, but a
    more complicated lens, with one dominant elliptical SIE and
    one or more perturbing elliptical SIEs, plus a circular NFW
    \citep{1996ApJ...462..563N,1997ApJ...490..493N} to represent
    the intergalactic mass.
\end{enumerate}

Formulas for the lenses appear in \cite{2001astro.ph..2341K}. The SIE
lenses follow equations (33--35) of that work, with core radius set to
zero.  The NFW lens is in equations (48) and (50), while shear is the
$\gamma$ term in equation (76).

\subsection{Some example models} \label{sec:example_models}

The modelers proposed a total of 129 models for the 29 sims in the
challenge.  Figures \ref{fig:6941} to \ref{fig:6919} show eight of
models in some detail.

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time.png}
  }
  \caption[result 6941 (ASW000102p)]{Sim ASW000102p and a model.  A
    simple configuration; the model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time.png}
  }
  \caption[result 6975 (ASW000195x)]{Sim ASW000195x and a
    model.}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time.png}
  }
  \caption[result 6937 (ASW0000vqg)]{Sim ASW0000vqg and a model.}
  \label{fig:6937}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6990_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6990_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6990_mass}
    \includegraphics[width=0.45\textwidth]{fig/006990_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6990_cont}
    \includegraphics[width=0.45\textwidth]{fig/006990_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6990_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006990_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6990_atime}
    \includegraphics[width=0.45\textwidth]{fig/006990_arr_time.png}
  }

  \caption[result 6990 (ASW0004oux)]{Sim ASW0004oux and a model.}
  \label{fig:6990}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6915_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6915_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6915_mass}
    \includegraphics[width=0.45\textwidth]{fig/006915_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6915_cont}
    \includegraphics[width=0.45\textwidth]{fig/006915_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6915_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006915_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6915_atime}
    \includegraphics[width=0.45\textwidth]{fig/006915_arr_time.png}
  }

  \caption[result 6915 (ASW0001hpf)]{Sim ASW0001hpf and a model. Inclined quad.}
  \label{fig:6915}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7022_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7022_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:7022_mass}
    \includegraphics[width=0.45\textwidth]{fig/007022_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7022_cont}
    \includegraphics[width=0.45\textwidth]{fig/007022_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7022_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007022_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:7022_atime}
    \includegraphics[width=0.45\textwidth]{fig/007022_arr_time.png}
  }

  \caption[result 7022 (ASW0000h2m)]{Sim ASW0000h2m and a model.  The
    model input appears in the middle panel of Figure
    \ref{fig:input-spag}.}
  \label{fig:7022}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7025_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7025_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:7025_mass}
    \includegraphics[width=0.45\textwidth]{fig/007025_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7025_cont}
    \includegraphics[width=0.45\textwidth]{fig/007025_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7025_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007025_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:7025_atime}
    \includegraphics[width=0.45\textwidth]{fig/007025_arr_time.png}
  }

  \caption[result 7025 (ASW0000h2m)]{Sim ASW0000h2m and another model.  The image parities in this case were incorrectly identified.}
  \label{fig:7025}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa.png}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv.png}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass.png}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti.png}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl.png}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time.png}
  }
  \caption[result 6919 (ASW0002z6f)]{Sim ASW0002z6f and a model.  The
    model input appears in the bottom panel of Figure
    \ref{fig:input-spag}. An incipient quad}
  \label{fig:6919}
\end{figure}
